SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-16 paper/abstract.tex
second half of the intro

In biology, there are several questions that translate to combinatorial
search. For example, vesicle traffic systems that move cargo within
eukaryotic cells have been proposed to exhibit several graph properties
such as three connectivity. These properties are consequences of underlying
biophysical constraints. A natural question for biologists is: what are all
possible networks for various combinations of those properties? In this
paper, we present SAT/QBF encodings of the properties over vesicle traffic
systems and a tool that searches for the networks that satisfies the
properties using SAT/QBF solvers. In our experiments, we show that our tool
can search for networks of sizes that are considered to be relevant by
biologists.

>>>>

In biology, there are several questions that translate to combinatorial
search. For example, vesicle traffic systems that move cargo within
eukaryotic cells have been proposed to exhibit several graph properties
such as three connectivity. These properties are consequences of underlying
biophysical constraints. A natural question for biologists is: what are all
possible networks for various combinations of those properties? In this
paper, we present novel SAT encodings of the properties over vesicle traffic
systems and a tool that searches for the networks that satisfies the
properties using SAT solvers. In our experiments, we show that our tool
can search for networks of sizes that are considered to be relevant by
biologists.

### 2017-06-16 paper/intro.tex
added
second half of the intro

@@

@@

>>>>

Total two pages

\begin{itemize}
\item \mukund{BIO motivation ( 1 paragraph ) }

\item \srivas{BIO to Graph problem ( a couple of paragraph) }

\item \srivas{Graph to previous encoding}

\end{itemize}

% \noindent

@@

vesicle traffic systems(VTS)

@@

In this paper, we have developed a novel SAT encoding for
searching a VTS that satisfy the given properties.
%
We improved the encoding of some of the conditions for VTSs.
%
In the earlier implementation, reachability was encoded as
by enumeration of paths.
%
In our encoding, we have recursively defined the reachability condition
such that that we avoid exponential enumeration.
%
We have also encoded $k$-connectivity in the similar fashion and
avoided a blowup in the formula size.
%

We have implemented the encoding using Z3~\cite{z3} python API and searched for
VTS satisfying various properties upto size \ankit{....} nodes as compare
earlier tool that could only search graph upto size 6 nodes.
%
Since most VTSs in the cells are less than \ankit{....} nodes,
our tool will be useful for biologists to study VTSs.
%
Furthermore, our encoding supports several variations of
the conditions.

The following are the contributions of this work:
\begin{itemize}
\item We have added novel encoding reachability and 3-4 connectivity
\item Direct encoding into the SAT solver
\item A user friendly and scalable tool based on well known SMT solver Z3
\end{itemize}
